\subsection{Empanadas}
\subsubsection{Filling (Pino)}
\begin{ingredients}
	\item 1kg minced meat
	\item 2kg onion, diced
	\item ??? salt
	\item 2tbsp paprika
	\item 2tbsp cumin
	\item 2tbsp oregano
	\item 300g raisins
\end{ingredients}
\begin{enumerate}
	\item Oil up a large pot, set to medium heat. Once it's hot, slowly add the onions.
	\item Once the onion becomes transparent, add seasonings and keep cooking for another 30-40 minutes. Add water as needed to keep the filling from drying or burning.
	\item Once the onion comes apart easily between your fingers, add the meat and keep cooking for another 15 minutes.
	\item Add raisins and keep the pot on the stove until the raisins rehydrate.
	\item Remove from fire and let it cool.
\end{enumerate}
\subsubsection{Dough}
\begin{ingredients}
	\item 500g flour
	\item 1 large egg
	\item 1tsp salt
	\item 70cc white wine
	\item 80g melted butter
	\item 150g hot water
\end{ingredients}
\begin{enumerate}
	\item Mix all ingredients in a bowl.
	\item Knead until elastic.
	\item Wrap in plastic foil and refrigerate for an hour.
\end{enumerate}
\subsubsection{Putting it All Together}
\begin{ingredients}
	\item egg wash
	\item 2 boiled eggs
	\item 8 black olives
	\item empanada dough
	\item pino
\end{ingredients}
\begin{enumerate}
	\item Heat oven to ???ºC.
	\item Peel and cut each egg into 4 pieces.
	\item Cut dough into 8 pieces.
	\item Flatten the dough using a rolling in until ~2mm thick.
	\item Apply egg wash along the edge of the disks.
	\item Put the filling at the center lening towards you.
	\item Add an olive and a piece of egg into each empanada.
	\item Close the dough around the filling and press lightly on the edges.
	\item Fold the dough towards the empanada. Tip: fold as closely to the filling as possible for best results.
	\item Move the empanadas into a tray, apply egg wash on top, and put into oven.
	\item Bake the empanadas for one hour, then remove and let cool.
\end{enumerate}

